---
title: "Privat vs Offentlig"
format: pdf
editor: visual
---

# Private vs public

```{r, include = FALSE, warning=FALSE}
# Nødvendige pakker
library(readr) # reading different file formats
library(readxl) # reading xlsx
library(dplyr) # tidying the datasets
library(rsample) # splitting data into testing and training
library(rpart) # CART
library(rpart.plot) # CART plotting 
library(caret) # making confusion matrix
library(skimr)
library(tidyverse) 
library(openxlsx)
```

As a part of the task we are going to try to differentiate between public and private entities.

```{r, message=FALSE}
# Loading the data we are going to use
transport_enheter_alle <- read_excel("data/transport_enheter_alle.xlsx")
tran_enheter_status <- read_excel("data/tran_enheter_narm.xlsx")

```

Using this dataset we will try to make a model that can tell if a company is private or public

```{r}
# Making a loop that based on the industrial sector codes gives each entity a status
check_public_private <- function(sector_code) {
  public_sector_codes <- c(6100, 6500, 1110, 1120, 1510, 1520)
  private_sector_codes <- c(2100, 2300, 2500, 3100, 3200, 3500, 3600, 3900, 4100, 4300, 4500, 4900, 5500, 5700, 8200, 8300, 8500)

  if (as.numeric(sector_code) %in% public_sector_codes) {
    return("Public")
  } else if (as.numeric(sector_code) %in% private_sector_codes) {
    return("Private")
  } else {
    return("Unknown")
  }
}

# Create an empty vector to store results
company_status <- vector("character", nrow(tran_enheter_status))

# Loop through each row and check public/private status
for (i in 1:nrow(tran_enheter_status)) {
  company_status[i] <- check_public_private(tran_enheter_status$institusjonell_sektorkode[i])
}

# Add the company_status information back to the dataset
tran_enheter_status$status <- company_status

# Print the updated dataset
print(tran_enheter_status)
```

Remove all text from the dataset to try and cluster based on the organisation number, sectorcodes and institutional sectorcodes.

```{r}
tran_enheter_num <- tran_enheter_status %>% 
  select(-c(navn, organisasjonsform_kode, organisasjonsform_beskrivelse, naeringskode_beskrivelse, hjemmeside, institusjonell_sektorkode_beskrivelse, overordnet_enhet, status))

test <- tran_enheter_staus%>% 
  filter(institusjonell_sektorkode %in% c(0))

table(test$organisasjonsform_beskrivelse)

```

Saving all of the used datasets to my computer so they are easier to access for the others. And making a dataset where the unkown are removed, these largely consist of foreign entities registered in Norway and bankruptcy estates

```{r}
write.xlsx(tran_enheter_status, "data/tran_enheter_status.xlsx")

# make a dataset that removes the unknown from the status variable
tran_enheter_unknownrm <- tran_enheter_status %>% 
  filter(!status %in% c("Unknown"))

# save this dataset
write.xlsx(tran_enheter_unknownrm, "data/tran_enheter_unknownrm.xlsx")

```

