---
title: "ISS1337"
author: "Vilde"
format: html
---

```{r}
#| eval: false
#install.packages("tinytex")
library(tinytex)
library(dplyr)
library(tidyverse)
library(readr)
library(readxl)
library(shiny)
library(aws.alexa)
library(gtrendsR)
#install.packages("readxl")
library(readxl)
library(writexl)
```

Import the dataset with all public entitites
```{r}
df <- read_excel("all_public_entities.xlsx")

column_names <- colnames(df)
print(column_names)
```

With problems with nordic letters, type Sys.setlocale(locale="no_NO") into the Console


How to select a sector
In the grep-function, add a word that describes your sector in general. It is the column`nkode1_beskrivelse` that contains a description that the dataset can be sorted on.

```{r}
matches_separate_word <- grep("\\btransport\\b|\\bruter\\b", df$`nkode1_beskrivelse`, ignore.case = TRUE, value = TRUE)
matches_as_part_of_word <- grep("transport|ruter", df$`nkode1_beskrivelse`, ignore.case = TRUE, value = TRUE)
all_matches <- unique(c(matches_separate_word, matches_as_part_of_word))
print(all_matches)
```
```{r}
filtered_df <- df[df$nkode1_beskrivelse %in% all_matches, ]
```

Add some well known transport companies manually. They have in common that nkode1_beskrivelse=="Offentlig administrasjon tilknyttet næringsvirksomhet og arbeidsmarked", and nkode2_beskrivelse == "Kommuneforvaltningen" so transport is neither mentioned.
```{r}
ruter <- df[df$Navn == "RUTER AS",]
atb <- df[df$Navn == "ATB AS",]	

filtered_df <- rbind(filtered_df, ruter)
filtered_df <- rbind(filtered_df, atb)

```



See that some transport companies show up with theese details. Transport or no other word that identifies the sector is avaiable
```{r}
rar <- df %>%
  filter(nkode1_beskrivelse =="Offentlig administrasjon tilknyttet næringsvirksomhet og arbeidsmarked" & `Institusjonell sektorkode.beskrivelse` == "Kommuneforvaltningen")

```

Saving dataset so it can be uploaded to Github
```{r}
#library(writexl)
#write_xlsx(filtered_df,"C:\\Users\\Shelg\\Documents\\Summercourse\\ISSSV\\public_transport_companies.xlsx")
```

Make two datasets, one with entities with websites and the other without
```{r}
no_web <- filtered_df %>%
  filter(is.na(Hjemmeside))

has_web <- filtered_df %>%
  filter(complete.cases(Hjemmeside))
```








```{r}

#install.packages("writexl")
library(writexl)

```



